\documentclass[11pt,a4paper]{article}

% Packages
\usepackage[margin=0.7in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{xcolor}

% Remove page numbers
\pagestyle{empty}

% Section formatting with horizontal rule
\titleformat{\section}{\large\bfseries\scshape}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{12pt}{6pt}

% Hyperlink setup
\hypersetup{
    colorlinks=true,
    linkcolor=black,
    urlcolor=blue!70!black,
    pdfborder={0 0 0}
}

% Custom commands
\newcommand{\resumeItem}[1]{\item #1}
\newcommand{\jobentry}[3]{%
    \noindent\textbf{#1} \hfill \textit{#2}\\
    \textit{#3}
}

\begin{document}

% ===== HEADER =====
\begin{center}
    {\LARGE\textbf{Aldana Melani Correa}}\\[4pt]
    {\large\textbf{C++ Software Developer}}\\[6pt]
    \href{mailto:aldanacorrea99@gmail.com}{aldanacorrea99@gmail.com} --- (+549) 351 789 2061 --- Argentina\\[2pt]
    \href{https://linkedin.com/in/aldanamelanicorrea}{linkedin.com/in/aldanamelanicorrea} ---
    \href{https://github.com/AldiMCorrea}{github.com/AldiMCorrea} ---
    \href{https://www.aldicorrea.com}{www.aldicorrea.com}
\end{center}

% ===== PROFESSIONAL PROFILE =====
\section{Professional Profile}
C++ Software Developer with 5+ years of experience in safety-critical medical systems and real-time applications. Proficient in modern C++ (C++11/14/17), design patterns, multithreading, and performance optimization. Strong track record building high-reliability software on ARM platforms using QNX RTOS and embedded Linux. Experienced in full development lifecycle from low-level driver development to Qt/QML-based user interfaces and system-level debugging.

% ===== WORK EXPERIENCE =====
\section{Work Experience}

\jobentry{Software and Firmware Developer}{Apr 2023 -- Present}{TECME S.A. -- Argentina}
\begin{itemize}[leftmargin=*, nosep, topsep=4pt]
    \resumeItem{Developed and maintained mission-critical firmware (IEC 62304 compliant) in C/C++ for a medical pulmonary ventilator, managing high-reliability tasks on QNX RTOS.}
    \resumeItem{Implemented real-time control logic (sensor reading, actuator control) and critical alarm systems using C++ Finite State Machines (FSMs) for various ventilation modes.}
    \resumeItem{Designed, implemented, and maintained low-level C drivers for the Toradex i.MX6 Quad Core (ARM Cortex-A9) platform, interfacing with peripherals (I2C, SPI, ADC) and participating in board bring-up.}
    \resumeItem{Integrated Qt/QML-based HMI with C++ control backend, establishing communication API for real-time data visualization and alarm propagation.}
    \resumeItem{Developed and maintained robust unit testing suite (GoogleTest/CppUnit) for C++ modules, ensuring code quality, reliability, and regression-free development.}
    \resumeItem{Automated software internationalization (i18n) pipeline by developing Python scripts consuming AI-based translation APIs for UI strings.}
    \resumeItem{Developed code-generation (scaffolding) tools in C++ and Python to auto-generate system parameters and boilerplate code, ensuring consistency with MVVM architecture.}
    \resumeItem{Performed system-level debugging, including UART/RS-232 communication analysis.}
\end{itemize}

\vspace{6pt}

\jobentry{Firmware Developer}{May 2021 -- Jun 2022}{RUF -- Functional Utility Robotics -- Argentina}
\begin{itemize}[leftmargin=*, nosep, topsep=4pt]
    \resumeItem{Developed firmware for smart plugs designed for remote security monitoring via cameras.}
    \resumeItem{Established communication between companies and international technicians to streamline microcontroller development and research.}
    \resumeItem{Designed solid programming and flashing structure for multiple microcontrollers (ESP12, ESP32, ESP8266, RTL) using C/C++, Espressif SDK, and RTOS.}
    \resumeItem{Created technical business documentation for each process; managed version control with GitHub/GitLab using Scrum methodology.}
\end{itemize}

\vspace{6pt}

\jobentry{Research \& Development Intern}{Mar 2021 -- Dec 2023}{UTN -- National Technological University -- Argentina}
\begin{itemize}[leftmargin=*, nosep, topsep=4pt]
    \resumeItem{Developed electrical measurement equipment with remote communication and real-time data transmission for residential power networks.}
    \resumeItem{Used embedded systems tools (ESP microcontrollers) with power, current, and voltage sensors.}
    \resumeItem{Achieved optimization, efficiency, and energy control monitoring for the final product.}
\end{itemize}

% ===== EDUCATION =====
\section{Education}

\noindent\textbf{Electronic Engineering} \hfill 2019 -- 2024\\
\textit{National Technological University (UTN) -- C\'{o}rdoba, Argentina}\\
In progress

\vspace{6pt}

\noindent\textbf{Software Engineering} \hfill 2024 -- Present\\
\textit{Universidad Siglo XXI -- Argentina}\\
In progress

% ===== SKILLS & COMPETENCIES =====
\section{Skills \& Competencies}

\noindent\textbf{Programming:}
\begin{itemize}[leftmargin=*, nosep, topsep=2pt]
    \item Modern C++ (C++11/14/17) and STL
    \item Design Patterns and SOLID Principles
    \item Multi-threaded and Concurrent Programming
    \item Memory Management, RAII and Smart Pointers
    \item Performance Optimization and Profiling
    \item Cross-platform Development (Windows, Linux, QNX)
\end{itemize}

\vspace{4pt}

\noindent\textbf{Professional:}
\begin{itemize}[leftmargin=*, nosep, topsep=2pt]
    \item Agile and Scrum Methodologies
    \item Code Review and Mentoring
    \item Problem-solving and Analytical Thinking
    \item Effective Communication and Collaboration
\end{itemize}

% ===== CERTIFICATIONS =====
\section{Certifications}

\begin{itemize}[leftmargin=*, nosep, topsep=2pt]
    \item \textbf{QNX Real-Time Operating System} -- BlackBerry QNX
    \item \textbf{Object-Oriented Programming in C++} -- Udemy
    \item \textbf{Implantable Electronic Devices and Medical Applications} -- EAMTA (Argentina School of Micro-NanoElectronics, Technology and Applications)
    \item \textbf{Kali Linux for Ethical Hacking} -- Udemy
    \item \textbf{Advanced C Programming} -- Noble Work Foundation
\end{itemize}

\end{document}
